Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-02 Latex/journal_v1/V4/pr.tex
latex .

Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data.
Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
Moreover, all O-RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ o-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary value that illustrates whether RU $r$ served the $i^{th}$ UE allocate to $s^{th}$ slice or not. Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

>>>>

Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ multi-antenna O-RU that are shared between slices. Each O-RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data.
Also $\mathcal{R} = \{ r | r\in 1,2,...,R \}$ depicts the set of O-RUs.
Moreover, all O-RUs, have access to the all PRBs.
Coordinated multipoint (CoMP) system is considered here. 
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ o-RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary value that illustrates whether RU $r$ served the $i^{th}$ UE allocate to $s^{th}$ slice or not. Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.
